### 2014-11-13 motivation.tex
Minor edit to where footnote is placed

Consider the execution shown in Figure~\ref{fig:unsafeWithdrawAnomaly}. Assume
that all operations in the figure are on the same bank account object with the
initial balance being zero. Session 1 performs a \cf{deposit} of 100, followed
by a \cf{withdraw} of 80 in the same session. The \cf{withdraw} operation
witnesses\footnote{Although visibility and session
order relations relate effects, we have abused the notation in these examples
to relate operations, with the idea that the relations relate the effect
emitted by those operations} the deposit and succeeds. Subsequently, session 2 perform a \cf{withdraw}
operation, but importantly, due to eventual consistency, only witnesses the
\cf{deposit} from session 1, but not the subsequent withdraw. Hence, this
\cf{withdraw} also \emph{incorrectly} succeeds, violating the integrity
constraint. A subsequent \cf{getBalance} operation, that happens to witness all
the previous operations, would report a negative balance.

>>>>

Consider the execution shown in Figure~\ref{fig:unsafeWithdrawAnomaly}. Assume
that all operations in the figure are on the same bank account object with the
initial balance being zero. Session 1 performs a \cf{deposit} of 100, followed
by a \cf{withdraw} of 80 in the same session. The \cf{withdraw} operation
witnesses the deposit and succeeds\footnote{Although visibility and session
order relations relate effects, we have abused the notation in these examples
to relate operations, with the idea that the relations relate the effect
emitted by those operations}. Subsequently, session 2 perform a \cf{withdraw}
operation, but importantly, due to eventual consistency, only witnesses the
\cf{deposit} from session 1, but not the subsequent withdraw. Hence, this
\cf{withdraw} also \emph{incorrectly} succeeds, violating the integrity
constraint. A subsequent \cf{getBalance} operation, that happens to witness all
the previous operations, would report a negative balance.
